Measuring causal influence with\\ back-to-back regression

### 2019-05-22 paper/meg_exps.tex
meg_exps

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a truncated regularization. Truncation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
  G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
\end{equation}
\begin{equation}
\hat X_{test} = Y_{test} \cdot G^T
\end{equation} where $\left(train,test\right)$ are partitions of the data.

\subsubsection{Second-level statistics}

The three types of analyses were implemented for each subject and each time
sample independently.  To estimate the reliability of these estimates in the
population, we tested, using one-sample $t$-test whether the distribution of
the estimated contribution of each factor different from baseline ($t=-100$ms),
as $\text{t-test}(\hat E_{t=-100} - \hat E_{\tau})$, with $\tau \in $ 150ms and
400ms respectively

>>>>

\paragraph{Back-to-back regression} We adapted back-to-back regression with two
changes. First, to avoid getting a slightly positively-biased estimate of the
factors contributing to the MEG signal, we swap the Tikhonov regularization of
the first regression $G$ with a truncated regularization. Truncation was fitted
 by maximum likelihood estimate, as implemented in scikit-learn principal
 component analysis. Second, to minimize the variance increase induced by
 bagging, we computed the inverse regularized covariance matrices outside
 bagging:
\begin{equation}
  G = (Y^T Y+\lambda_Y I)^{-1} Y_{train}^T X_{train}
\end{equation}
\begin{equation}
\hat X_{test} = Y_{test} \cdot G^T
\end{equation} where $\left(train,test\right)$ are partitions of the data.
%
% \subsubsection{Second-level statistics}
%
% The three types of analyses were implemented for each subject and each time
% sample independently.  To estimate the reliability of these estimates in the
% population, we tested, using one-sample $t$-test whether the distribution of
% the estimated contribution of each factor different from baseline ($t=-100$ms),
% as $\text{t-test}(\hat E_{t=-100} - \hat E_{\tau})$, with $\tau \in $ 150ms and
% 400ms respectively
